A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-05-19 paper/paper.tex
Don't microtype
bigskip before summary of experiments

\usepackage{ijcai17}
\usepackage{times}
\usepackage{graphicx}
\usepackage{cleveref}
\usepackage{microtype}
\usepackage{booktabs}

@@

To summarise these experimental results, we find that \McSplit\ improves on the
previous state of the art by more than an order of magnitude for small,
unlabelled graphs.  On a benchmark suite of larger instances, the
\McSplit{$\downarrow$} variant of the algorithm comfortably outperforms the
state of the art.  On labelled instances, the clique encoding remains the
strongest solver, except on the most trivial instances---particularly where
there is no requirement for the common subgraph to be connected.

>>>>

\usepackage{ijcai17}
\usepackage{times}
\usepackage{graphicx}
\usepackage{cleveref}
%\usepackage{microtype}
\usepackage{booktabs}

@@

\bigskip

Overall, we find that \McSplit\ improves on the
previous state of the art by more than an order of magnitude for small,
unlabelled graphs.  On a benchmark suite of larger instances, the
\McSplit{$\downarrow$} variant of the algorithm comfortably outperforms the
state of the art.  On labelled instances, the clique encoding remains the
strongest solver, except on the most trivial instances---particularly where
there is no requirement for the common subgraph to be connected.
